Computing in the Field of Rationals

### 2012-02-27 rational.tex
multiplicative

%subcode-inline{bnf-inline} name langRev
%! swap+ = \mathit{swap}^+
%! swap* = \mathit{swap}^*
%! dagger =  ^{\dagger}
%! assocl+ = \mathit{assocl}^+
%! assocr+ = \mathit{assocr}^+
%! assocl* = \mathit{assocl}^*
%! assocr* = \mathit{assocr}^*
%! identr* = \mathit{uniti}
%! identl* = \mathit{unite}
%! dist = \mathit{distrib}
%! factor = \mathit{factor}
%! eta+ = \eta^+
%! eps+ = \epsilon^+
%! eta* = \eta^*
%! eps* = \epsilon^*
%! (o) = \fatsemi
%! (;) = \fatsemi
%! (*) = \times
%! (+) = +

@@

@@

@@

>>>>

%subcode-inline{bnf-inline} name langRev
%! swap+ = \mathit{swap}^+
%! swap* = \mathit{swap}^*
%! dagger =  ^{\dagger}
%! assocl+ = \mathit{assocl}^+
%! assocr+ = \mathit{assocr}^+
%! assocl* = \mathit{assocl}^*
%! assocr* = \mathit{assocr}^*
%! identr* = \mathit{uniti}
%! identl* = \mathit{unite}
%! dist = \mathit{distrib}
%! factor = \mathit{factor}
%! eta+ = \eta^+
%! eps+ = \epsilon^+
%! eta* = \eta^*
%! ^^^ = ^{-1}
%! eps* = \epsilon^*
%! (o) = \fatsemi
%! (;) = \fatsemi
%! (*) = \times
%! (+) = +

@@

\begin{proposition}[Logical Reversibility]
\label{prop:logrev}
{{c v |--> v'}} iff {{c{dagger} v' |--> v}}.
\end{proposition}

\begin{proposition}[Groupoid]
\label{prop:groupoid}
{{langRev}} is a groupoid. 
\end{proposition}

\begin{proposition}
\label{prop:groupoid}
{{langRev}} is a dagger symmetric monoidal category. 
\end{proposition}

@@

%subcode{bnf} include main
% Value Types, b = ... | b^^^
% Values, v = ... | v^^^
%
% Isomorphisms, iso &=& ... | eta* | eps*

%subcode{opsem} include main
% eta* &: 1 <-> b^^^ * b :& eps*

%subcode{proof} include main
%@ |- v : b
%@@ |- v^^^ : b^^^

Note that we will freely write {{b^^^}} as {{1/b}} and {{a*b^^^}} as
{{a/b}}.

\paragraph*{Unification.}

\paragraph*{Entanglement.}

\paragraph*{Coherence.}

\paragraph*{Annihilation.}

\paragraph*{Zero Information.}

@@

\begin{proposition}[Logical Reversibility]
\label{prop:logrev}
{{c v |--> v'}} iff {{c{dagger} v' |--> v}}.
\end{proposition}

\begin{proposition}[Groupoid]
\label{prop:groupoid}
{{langRevEE}} is a groupoid. 
\end{proposition}

\begin{proposition}
\label{prop:groupoid}
{{langRev}} is a Dagger Symmetric Monoidal Closed Category.
\end{proposition}

Note: We use `Monoidal Closed' in the sense of Compact Closed. While
the category has an multiplicative tensor that distributes over an
additive tensor, it does not have injections or projections and hence
does not have categorical sums and products.
